\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\pagenumbering{gobble}
\usepackage{microtype}
\usepackage{multicol}
\usepackage[colorlinks = true, urlcolor = blue]{hyperref}
\urlstyle{rm}
\usepackage{tabularx}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\usepackage[left=1.5cm,right=1.5cm,top=1cm,bottom=1cm]{geometry}
\author{Xinyu Lu}
\title{Curriculum Vitae }
\begin{document}
\begin{center}
\begin{LARGE}
\textbf{CURRICULUM VITAE}
\end{LARGE}\\
\vspace{0.1\baselineskip}
\begin{large}
\begin{tabularx}{\textwidth}{LCR}
\href{mailto:cicerolu@g.ucla.edu}{cicerolu@g.ucla.edu} && 433 Kelton Avenue, LA, CA
\end{tabularx}
\end{large}\\
\vspace{-0.6\baselineskip}
\rule{\textwidth}{0.5pt}
\end{center}
\vspace*{0.5\baselineskip}
\begin{tabularx}{\textwidth}{Lp{10cm}R}
%\textsc{Objective} & \multicolumn{2}{p{13.75cm}}{Aiming for a position to apply Machine Learning and Software Engineering} \\
\textsc{Contact Info} &\textbf{Xinyu (Cicero) Lu} &  (424)-666-5882 \\

\textsc{Research Interest} & \multicolumn{2}{p{13.75cm}} {I am interested in studying hierarchical triple systems in stellar evolutions and exoplanet orbital mechanics.} \\  
\\
\textsc{Education} &\textbf{University of California, Los Angeles} & \\
& 9/2013 - 6/2017(Expected)\\
\rule{0pt}{10pt}
%& \textsl{ } & 9/2013 - 6/2017\\
\rule{0pt}{12pt}   
& \multicolumn{2}{p{13.75cm}}{$\bullet\;$Major in Physics and Minor in Mathematics.}\\
%& \multicolumn{2}{p{13.75cm}}{$\bullet\;$Major GPA: 3.4 , Major Upper Div: 3.6, Overall GPA: 3.49.}\\
& \multicolumn{2}{p{13.75cm}}{$\bullet\;$Enrolled in College Honors Program.}\\
\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textsc{Research } &\textbf{Supernova Kicks in Hierarchical Triple System} & UCLA\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%=======Research 1 ===========%
%\rule{0pt}{10pt}
\textsc{Experience} & \textsl{Undergraduate Researcher,}  PI: Smadar Naoz & 11/2014 - Present\\
\rule{0pt}{10pt}   
& \multicolumn{2}{p{13.75cm}}{$\bullet\;$ 
Derived the effect of supernova natal kick on the triple body orbital parameters}\\
& \multicolumn{2}{p{13.75cm}}{$\bullet\;$ Predicted the survival rate of low-mass X-ray in binaries(and other compact systems) and their orbital parameters distribution}\\
& \multicolumn{2}{p{13.75cm}}{$\bullet\;$Developed analytical results that set the constraints on maximum supernova kicks in triple star systems}\\
& \multicolumn{2}{p{13.75cm}}{$\bullet\;$ Implemented Monte Carlos methods to study the parameter space of impacts of supernova kicks on triple star systems}\\
%\rule{0pt}{12pt}
\\
%& \multicolumn{2}{p{13.75cm}}{$\bullet\;$ Publication in prep.}\\
%=======Research 2 ===========%
&\textbf{Gravitational Lensing} & UCLA\\
\rule{0pt}{9pt}
& \textsl{Undergraduate Research Assistant,} PI: Tommaso Treu & 7/2016 - present \\
\rule{0pt}{10pt}   
& \multicolumn{2}{p{13.75cm}}{$\bullet\;$Compiled a database for lensed quasars. $\bullet\;$ Modeled lensed quasars with gaussian models in Python.}\\
\\
%=======Research 3 ===========%
& \textbf{Physical Properties of Merging Galaxies} &UCLA\\
\rule{0pt}{9pt}
& \textsl{Senior Thesis,} PI: Alice Shapley & 9/2016 - present\\
\rule{0pt}{10pt}   
& \multicolumn{2}{p{13.75cm}}{$\bullet\;$ Used Mosfire 2D spectrograph to study the physical properties of merging galaxies.}\\
\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% SCHOLARSHIP  %%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textsc{Scholarships}  & \multicolumn{2}{p{13.75cm}}{\textbf{UCLA Undergraduate Research Scholars Program Scholarship}: Awarded Scholarship by Van Tree Foundation, Sept. 2016 - July 2017}\\
\rule{0pt}{12pt}
& \multicolumn{2}{p{13.75cm}}{\textbf{UCLA Honors 2015 Summer Research Scholarship Recipient}: Awarded Stone Scholarship fund for summer research, Jun. 2015 - Sept. 2016 }\\
\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%      PUBLICATION  %%%%%%%%%%%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textsc{Publications} & \multicolumn{2}{p{13.75cm}}{Kilpatrick, Charles D.; Foley, Ryan J.; Abramson, Louis E.; Pan, Yen-Chen; \textbf{Lu, Cicero-Xinyu}; Williams, Peter; Treu, Tommaso; Siebert, Matthew R.; Fassnacht, Christopher D.; Max, Claire E.	"On the Progenitor of the Type IIb Supernova 2016gkg" \textsl{Monthly Notices of the Royal Astronomical Society}, submitted.}\\
\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% SELECT PRESENTATIONS  %%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textsc{Selected Presentations} & \multicolumn{2}{p{13.75cm}}{Supernova Kicks in Hierarchical Triple Systems, \textsl{Conferences for Undergraduate Women in Physics}, San Diego, California, Jan. 2016}\\
\rule{0pt}{12pt}
&\multicolumn{2}{p{13.75cm}}{Supernova Kicks in Hierarchical Triple Systems, \textsl{Undergraduate Research Poster Day}, UCLA, California, Jun. 2016}\\
\\
%\rule{0pt}{12pt}
% \rule{0pt}{14pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% Awards  %%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textsc{Competition Awards} &{\textbf{Mathematical Contest in Modeling}} & Global Contest\\
\rule{0pt}{10pt}
 & {Meritorious Winner of 2015 (Top 10\% globally)} & 3/2015 \\
 & \multicolumn{2}{p{13.75cm}}{
$\bullet\;$Implemented Monte Carlo Algorithm and Greedy-like search algorithm; 
Modeling with Matlab and Mathematica with Bayes Analysis
}\\
\rule{0pt}{12pt}
& {\textbf{Teradata Hackathon}} & Los Angeles\\
&{Won 4th place} & 10/2015\\
& \multicolumn{2}{p{13.75cm}}{$\bullet\;$implemented Living place Optimizer with Python and Teradata REST API.}\\
\rule{0pt}{14pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% SKILLS            %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textsc{Skills} & \multicolumn{2}{p{13.75cm}}{\textbf{Python, MATLAB:} Scientific Plotting and Monte Carlos Processes.}\\
\textsc{} & \multicolumn{2}{p{13.75cm}}{\textbf{Mathematica:} Used for symbolic calculation in theoretical research.}\\
\textsc{} & \multicolumn{2}{p{13.75cm}}{\textbf{Machine Learning:} Familiar with algorithms, such as Linear/Logistic Regression, K-means clustering, Support Vector Machine, Principal Component analysis, Gaussian Mixture models.}\\
\\

\end{tabularx}
\end{document}